The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-30 paper.tex
Added angle to basic SonAngle diagram using tkz-euclide
Used package fixltx2e to add textsubscript rather than defining manually - this was raising complaints
Improved second diagram

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[table]{xcolor}    %for shading*
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{mathpazo}
\usepackage{tipa}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{linguex}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{slashbox}	
\usepackage{pifont}    %for pointing hand
\usepackage{arydshln}  %for dashed lines
\usepackage{rotating}  %for angled text
\usepackage{wasysym}   %for frowny face

@@

\makeatletter
\newcommand\textsubscript[1]{\@textsubscript{\selectfont#1}}
\def\@textsubscript#1{{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
\newcommand{\iep}{\textipa{1}}
\newcommand{\bet}{\textipa{B}}
\newcommand{\schwa}{\textipa{@}}

@@

\ex. \label{sonangle_picture} \begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
                      \node[left] at (0,3) {C$_1$}; 
                      \node[right] at (5,1) {C$_2$};
                      \node[right] at (5,6) {V};
    \coordinate (A) at (0,3);
    \coordinate (B) at (5,1);
    \coordinate (C) at (5,6);
\end{tikzpicture}

@@

Let us verify that {\sc Sonority Angle} does indeed reflect the two generalisations we wish to make:
first, that the smaller the sonority distance between C\textsubscript{1} and C\textsubscript{2},
the smaller the sonority angle.
Imagine fixing C\textsubscript{1} as in \ref{sonangle_picture} and raising the sonority of C\textsubscript{2}. Intuitively, this decreases the {\sc Sonority Angle}, comparing the two below.

\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
					 % left diagram
                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
                      \node[left] at  (0,3) {C$_1$}; 
                      \node[right] at (5,1) {C$_2$};
                      \node[right] at (5,6) {V};
					  % right diagram
                      \draw (20,4) -- (15,3) -- (20,6) ; % falling sonority
                      \node at (17.5, 4.0) {$\theta$}; % theta label for falling sonority
                      \node[left] at (15,3) {C$_1$}; 
                      \node[right] at (20,4) {C$_2$};
                      \node[right] at (20,6) {V};
\end{tikzpicture}

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[table]{xcolor}    %for shading*
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{mathpazo}
\usepackage{tipa}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{linguex}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usepackage{slashbox}	
\usepackage{pifont}    %for pointing hand
\usepackage{arydshln}  %for dashed lines
\usepackage{rotating}  %for angled text
\usepackage{wasysym}   %for frowny face

@@

\usepackage{fixltx2e}

%\makeatletter
%\newcommand\textsubscript[1]{\@textsubscript{\selectfont#1}}
%\def\@textsubscript#1{{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
\newcommand{\iep}{\textipa{1}}
\newcommand{\bet}{\textipa{B}}
\newcommand{\schwa}{\textipa{@}}

@@

\ex. Visual representation of {\sc Sonority Angle} \label{sonangle_picture}

\vspace{-3em}
\begin{center}
\begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
%                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
                      \node[left] at (0,3) {C$_1$}; 
                      \node[right] at (5,1) {C$_2$};
                      \node[right] at (5,6) {V};
    \coordinate (A) at (0,3);
    \coordinate (B) at (5,1);
    \coordinate (C) at (5,6);
\tkzMarkAngle[size=1.5cm](B,A,C)
\tkzLabelAngle[pos=2](B,A,C){$\theta$}
\end{tikzpicture} 
\end{center}

@@

Let us verify that {\sc Sonority Angle} does indeed reflect the two generalisations we wish to make: first, that the smaller the sonority distance between C\textsubscript{1} and C\textsubscript{2}, the smaller the sonority angle.

\ex. Illustration: keeping C\textsubscript{1} fixed, raising the sonority of C\textsubscript{2} decreases the {\sc Sonority Angle}.

\vspace{-5em}
\begin{center}
\begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,12) -- (-3, 0.5) ; % axis
                      \node at (-3, 13.0) {Sonority}; % axis label
					 % left diagram
    \coordinate (A) at (0,6); % pivot - C1
    \coordinate (B) at (15,2); % C2
    \coordinate (C) at (15,12); % V
    \draw (B) -- (A) -- (C);
	\tkzMarkAngle[size=3cm](B,A,C);
	\tkzLabelAngle[pos=4](B,A,C){$\theta_1$};
    \coordinate (D) at (15,8); % another C2
    \draw (D) -- (A);
	\tkzMarkAngle[size=6cm](D,A,C);
	\tkzLabelAngle[pos=8](D,A,C){$\theta_2$};

    \node[left] at  (A) {N}; 
    \node[right] at (B) {T};
    \node[right] at (C) {V};
    \node[right] at (D) {R};

    \draw [->,dotted] (B) -- (D);
\end{tikzpicture} 
\end{center}
